Demanding resources: Agreement of perceptions for challenge and resource characteristics

### 2022-10-07 SIOP2023/Counts/convergence.Rmd

author: 
  - name          : "John Kulas"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    email         : "jtkulas@ergreports.com"
  - name          : "Alicia Stachowski"
    affiliation   : "2"
  - name          : "Renata Garcia Prieto Palacios Roji"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "eRg"
  - id            : "2"
    institution   : "University of Wisconsin - Stout"
  - id            : "3"
    institution   : "PepsiCo"

@@

#r_refs("r-references.bib")
knitr::write_bib("r-references.bib")

@@

All analyses are focused on characteristics of work that are rated as being "relevant". Upon confirming that a work characteristic was relevant, respondents then also rated the extent to which that characteristic was percieved as a resources, challenge, and hindrance.

@@

Important to look not only at demands, but also the nature of the demand. Similar to the eustress/distress distinction, it would seem as though demands should be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand)[^bootsie].

>>>>

author: 
  - name          : "John Kulas"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    email         : "jtkulas@ergreports.com"
  - name          : "Alicia Stachowski"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "eRg"
  - id            : "2"
    institution   : "University of Wisconsin - Stout"

@@

r_refs("r-references.bib")
#knitr::write_bib("r-references.bib")

@@

All analyses are focused on characteristics of work that were rated as being "relevant" to the respondents' job. Upon confirming that a work characteristic was relevant, respondents then also rated the extent to which that characteristic was percieved as a resources, challenge, and hindrance.

@@

Our findings highlight the importance of dissociating the *nature* of job demands. Similar to the eustress/distress distinction [e.g., @selye1974stress], it would seem as though demands should be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand)[^bootsie].
